### 2021-09-12 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@de45ae8d78139046c161efbf0490595013cc49eb 🚀

We use data from the European metaweb assembled by Maiorano \emph{et
al.} (2020b), following the definition of the metaweb first introduced
by Dunne (2006), \emph{i.e.} an inventory of all possible interactions
within species from a spatially delimited pool. Notably the metaweb is
not a prediction of the food web at any specific locale within the
frontiers of the species pool -- in fact, these local food webs are
expected to have a subset of both the species and the interactions of
their metaweb (Poisot \emph{et al.} 2012). This being said, as the
metaweb represents the total of functional, phylogenetic, and
macroecological processes (Morales-Castilla \emph{et al.} 2015), it is
thus still worthy of ecological attention. We deduced the subgraph
corresponding to all mammals by matching species names in the original
network to the GBIF taxonomic backbone (GBIF Secretariat 2021) and
retaining all those who matched to mammals. This serves a dual purpose
1) to extract only mammals from the European network and 2) to match and
standardize species names when aggregating the different data sources
further downstream (which is an important consideration when combining
datasets Grenié \emph{et al.} (2021)). All nodes had valid matches to
GBIF at this step, and so this backbone is used for all name
reconciliation steps as outlined below.

>>>>

We use data from the European metaweb assembled by Maiorano \emph{et
al.} (2020b), following the definition of the metaweb first introduced
by Dunne (2006), \emph{i.e.} an inventory of all possible interactions
within species from a spatially delimited pool. Notably the metaweb is
not a prediction of the food web at any specific locale within the
frontiers of the species pool -- in fact, these local food webs are
expected to have a subset of both the species and the interactions of
their metaweb (Poisot \emph{et al.} 2012). This being said, as the
metaweb represents the total of functional, phylogenetic, and
macroecological processes (Morales-Castilla \emph{et al.} 2015), it is
thus still worthy of ecological attention. We deduced the subgraph
corresponding to all mammals by matching species names in the original
network to the GBIF taxonomic backbone (GBIF Secretariat 2021) and
retaining all those who matched to mammals. This serves a dual purpose
1) to extract only mammals from the European network and 2) to match and
standardize species names when aggregating the different data sources
further downstream (which is an important consideration when combining
datasets (Grenié \emph{et al.} 2021)). All nodes had valid matches to
GBIF at this step, and so this backbone is used for all name
reconciliation steps as outlined below.
